The Assembly of Black Hole Mass ad Luminosity Functions of High-redshift Quasars\\via Multiple Accretion Episodes

### 2022-09-28 ms.tex
version0928_1; integrated w/ ms0927_k

% \documentclass[linenumbers,preprint2,tighten,trackchanges]{aastex631}
%\documentclass[nolinenumbers,preprint2,tighten]{aastex631}
\hypersetup{filecolor=cyan,urlcolor=blue} %citecolor=green, linkcolor=red,
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{mathrsfs}

@@

\title{Constraining Black Hole Growth with High-z Quasar Observations}

@@

%%%%%%%
%    Fig. 1
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{seedBHMF_z.png}
\caption{
Mass distribution of seed BHs formed in quasar host galaxies at different redshifts ($50\lesssim z \lesssim 10$).
%Each panel includes a redshift span of 10, 
In each panel, the cumulative number distribution of BHs formed prior than the redshift interval is shown with green bars,
and the contribution from newly-born BHs during the interval are highlighted in magenta.
%with the newly formed BHs denoted by the hatched regions, 
%and the cumulative BHs formed previously by the blue region.
The majority of seed BHs form in the epoch of $20\lesssim z \lesssim 40$.
%The most vigorous seed formation epoches are in redshift ranges $z\sim$ $40-30$ and $30-20$.
Overall, the seed BH mass distribution is extended to $M_\bullet \gtrsim 10^5~\Msun$, 
imprinted with various pathways of parent halo assembly and environmental effects as discussed in Section~\ref{sec:seed}.
}
\label{fig:seedmf}
\end{figure*}

@@

Fig.~\ref{fig:seedmf} presents how the seed mass function is developed in each redshift interval.
The majority of seed BHs forms in the epoch of $20\lesssim z \lesssim 40$, and the distribution function is 
extended to $M_\bullet \gtrsim 10^5~\Msun$, imprinted with the halo assembly and environmental effects.

\orange{
Lastly, we note that in each parent halo, we consider purely the PopIII stellar remnants in the seed BH mass function construction,
neglecting the BHs formed by the second-generation PopII stars.
Formed in metal-enriched environments, PopII stellar remnants are more abundant but typically less massive.
They are likely to dominate the low mass end of the BHMF at $z\sim 6$,
thus not significantly contribute to the observable QLF and BHMF \citep{2022MNRAS.511..616T}.
}

%%%%%%%
%    Fig. 2
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=170mm]{scheme1.pdf}
\caption{\orange{
Schematical demonstration of the procedure to calculate the evolution of BH mass distribution from the earliest BH seed to $z=6$.
The checkpoints are spaced evenly with time interval $\tau$.
From time $T_0$ to $T_0+\tau$, 
the BH mass distribution evolves with $\Delta t=\tau$.
For a newly formed seed BH $M_{\rm i}$, the probability distribution function of BH mass is a delta function, 
and the growth time is $\Delta t = T_0+\tau-t_{\rm i}$.
The probability of a BH with mass $M_0$ (or $M_{\rm i}$) to grow to $M$ after $\Delta t$ is drew from the 
ERDF following Eq.~(\ref{eq:Pl}). 
Thus the evolution of BH mass distribution is reshaped iteratively 
plus taking account of the newly formed seeds if there are any.}
}
\label{fig:scheme}
\vspace{5mm}
\end{figure*}

% Figure 1 shows the BH seeds formed in progenitors of $\Mh = 10^{11}, 10^{12}$
\vspace{2mm}

\subsection{BH mass growth}
\label{sec:model}
With BH seeds planted, we study the evolution of the BH mass distribution until $z=6$. 
The growth model of each BH is characterized by a minimal number of free parameters, 
giving the accretion rate by
%
\begin{equation}
  \label{eq:mdot}
  \Mdot_\bullet = \lambda f(\Mbh) \Mdot_\mathrm{Edd} ,
\end{equation}
where $\lambda \equiv L/L_\mathrm{Edd}$ is the luminosity-based Eddington ratio,
and $\Mdot_\mathrm{Edd} \equiv L_{\mathrm{Edd}}/\eta_0 c^2$ is the Eddington accretion rate with a radiative efficiency of $\eta_0=0.1$ \citep{1973A&A....24..337S},
which is consistent with the value obtained from the Soltan-Paczy{\'n}ski argument \citep[e.g.,][]{2002MNRAS.335..965Y,2010ApJ...725..388C}.
On the basis of studies on the mass dependence of the radiative efficiency for AGNs at $z\lesssim$ 3 
\citep{2008MNRAS.390..561C,2012ApJ...749..187L,2014ApJ...786..104U}, 
we introduce a similar functional form of
%
\begin{equation}
\label{eq:f_M}
f(\Mbh) = \frac{2}{1+\left(\Mbh /M_{\bullet,c} \right)^\delta}, 
\end{equation}
%
where $M_{\bullet,c}=10^8~\Msun$ is adopted.
\orange{
From the viewpoint of galactic-scale gas supply,
this characteristic mass is in good agreement with the critical BH mass in \citet{2021ApJ...907...74T},
above which super-Eddington mass growth of the central BHs no longer happens as
galactic scale mass supply rates into the nuclear regions cannot be as large as the Eddington rates.
}
With a positive value of $\delta$, the BH growth at the high mass end is suppressed,
while the growth speed for less masssive BHs is accelerated.
In the limit of $\delta \ll 1$, where $f(\Mbh) \simeq 1$ is nearly independent of $M_{\bullet,c}$,
the model in Eq.~(\ref{eq:f_M}) reproduces an exponential growth with an $e$-folding timescale of
$t_{\rm S} =  \Mbh/\Mdot_{\mathrm{Edd}} \approx 45$ Myr (the so-called Salpeter timescale; \citealt{1964ApJ...140..796S}).

@@

\subsection{BH mass function}\label{sec:MF}

@@

\vspace{2mm}
%\section{Results}\label{sec:result}
\section{Results}\label{sec:fitting_result}

%\vspace{2mm}
%\subsection{Fitting Results}\label{sec:fitting_result}

%%%%%%%
%    Fig. 3
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=85mm]{f1_corner.pdf}
\includegraphics[width=85mm]{f2_corner.pdf}
\caption{
Two dimensional posterior distribution of all the model parameters with $\fseed=0.1$ and 0.01, 
along with the marginalized one dimensional projection.
% and the two dimensional distribution between every two parameters. 
The distribution of three parameters ($\tau$, $\lambda_0$, and $\alpha$) show single peaks,
displaying the convergence of those parameters.
The distribution of $\log\delta$ is relatively broader but suggests that the value of $\delta$
is sufficiently low and thus the mass-dependent growth model is excluded.
}
\label{fig:contour}
\vspace{5mm}
\end{figure*}
%

@@

%%%%%%%
%    Table. 1
%%%%%%%
\begin{deluxetable}{lcccccc}%[t!]
\tablecolumns{1}
\renewcommand\thetable{1} %! fix indexing
\tablewidth{0pt}
\tablecaption{Best-fit Parameters \label{tab:best_fits}} %!!!!
\tablehead{
  \colhead{$\fseed$}  & \colhead{$\tau$ (Myr)} & \colhead{$\delta$} &  \colhead{$\lambda_0$}  & \colhead{$\alpha$}  & \colhead{$\chi^2$}
}
\startdata
1.0    &  23.13 &    0.001    &   0.96    &   -0.06    &    15.77   \\
0.1    &  20.07 &    0.001    &   0.89    &    0.12    &    8.27    \\
0.01   &  18.76 &    0.055    &   0.87    &    0.20    &    6.21    \\
\enddata
\tablecomments{
The best-fit parameters optimized by MCMC sampling for different cases of $\fseed$.
The fitting performance is characterized by the relative magnitudes of the $\chi^2$ value.% (see Eq.~\ref{eq:chi2}).
}
\end{deluxetable}

@@

%%%%%%%
%    Fig. 4
%%%%%%%
\begin{figure*}
\centering
%\includegraphics[width=170mm]{fits_MF.png}
\includegraphics[width=85mm]{f1ndraw60MF_spread.pdf}\hspace{3mm}
\includegraphics[width=85mm]{f2ndraw60MF_spread.pdf}
\caption{
The BH mass function at $z=6$ with the best-fit parameters (black curve) and the $1\sigma$ spread (shaded region) for the cases with $\fseed=0.1$ (left) and $0.01$ (right). 
For comparison, the BHMF inferred by \citetalias{2010AJ....140..546W} is overlaid (blue curve and shaded region).
The data is used for the model parameter fitting.
%.The blue line shows the BHMF derived by \citet{2010AJ....140..546W}.
% error of observation
}
\label{fig:fitmf}
\end{figure*}

%%%%%%%
%    Fig. 5
%%%%%%%
\begin{figure*}
\centering
%\includegraphics[width=170mm]{fits_LF.png}
\includegraphics[width=85mm]{f1ndraw60LF_spread.pdf}\hspace{3mm}
\includegraphics[width=85mm]{f2ndraw60LF_spread.pdf}
\caption{
The unobscured quasar luminosity function at $z=6$ with the best-fit parameters (black solid line) and the $1\sigma$ spread for the cases with $\fseed=0.1$ (left) and $0.01$ (right).
The observed data (blue symbols) with error bars are taken from \citetalias{2018ApJ...869..150M} and is used for the model parameter fitting.
The upper bound of faint quasar number density is derived from the cumulative QLF presented in \citet{2022NatAs...6..850J}.
The X-ray QLF data in the faint end inferred from the $z\sim 5-6.1$ quasar sample in \citet{2019ApJ...884...19G} are denoted by orange symbols,
note that we conduct an extrapolation with quasar number densities scaling with $10^{-0.72\Delta z}$ at $z$ in $5-6$ \citep{2016ApJ...833..222J}.
For comparison, we show the intrinsic QLF predicted by our model in dashed lines.
}
\label{fig:fitlf}
\vspace{2mm}
\end{figure*}

@@

%%%%%%%
%    Fig. 6
%%%%%%%
\begin{figure*}
\centering
%\includegraphics[width=175mm]{BHMF_rhoz1.png}
\includegraphics[width=85mm]{MF.pdf}\hspace{5mm}
\includegraphics[width=81mm]{rhoM_comb.pdf}
\caption{
{\it Left panel}: BH mass functions predicted by the best-fit models at $z=6-10$,
including a fraction of $\fseed$ seeds evolving by our model assumption and the remaining ($1-\fseed$) fraction with no subsequent growth.
The solid (dashed) lines denote the cases with $\fseed=0.1$ (0.01).
{\it Right panel}: the cumulative mass density evolution for BHs in different mass ranges in a comoving volume, 
evaluated by the integration of the BHMF shown in the left panel.
The dashed-dotted line and open square symbols show the results from \citet{2022MNRAS.513..670N}.
The upper bound of accreted BH mass density from \citet{2013ApJ...778..130T} is denoted by black arrows.
% The evolutionary trend can be approximated as $\rho_\bullet (z) \propto 10^{k_M z}$, where $k_M\simeq -0.68$.
}
\label{fig:BHMF_rhoz}
\vspace{5mm}
\end{figure*}

@@

%%%%%%%
%  Table. 2
%%%%%%%
\begin{deluxetable*}{ccccccccccc}%[t!]
\tablecolumns{1}
\renewcommand\thetable{2} %! fix indexing
\tablewidth{0pt}
\tablecaption{Parametric Quasar Luminosity Function \label{tab:QLF_fit}}
\tablehead{
  & & \multicolumn{4}{c}{Unobscured QLF} && \multicolumn{4}{c}{Intrinsic QLF}  \\
  \cline{3-6} \cline{8-11}
  \colhead{Redshift} && \colhead{$\Phi^\ast$} & \colhead{$\Muv^\ast$} & \colhead{$\tilde \alpha$} & \colhead{$ \tilde \beta$}& &
  \colhead{$\Phi^\ast$} & \colhead{$\Muv^\ast$} & \colhead{$\tilde \alpha$} & \colhead{$\tilde \beta$}\\
  & & \colhead{(Gpc$^{-3}$ mag$^{-1}$)} & \colhead{(mag)} & & & &
  \colhead{(Gpc$^{-3}$ mag$^{-1}$)} & \colhead{(mag)} & &
}
\startdata
$z\sim 6$  && 46.5 & -23.62 & -1.33 & -2.57    && 89.2 & -23.73 & -1.59 & -2.67 \\
$z\sim 7$  && 6.98 & -23.70 & -1.61 & -2.82   && 12.4 & -23.85 & -1.87 & -2.92 \\
$z\sim 8$  && 1.18 & -23.80 & -1.83 & -3.02   && 1.91 & -23.98 & -2.08 & -3.12 \\
$z\sim 9$  && 0.268 & -23.80 & -1.98 & -3.18  && 0.429& -23.96 & -2.23 & -3.28 \\
$z\sim 10$ && 0.0841 & -23.68 & -2.01 & -3.30 && 0.144 & -23.82 & -2.35 & -3.40 \\
\enddata
\tablecomments{Parameters characterizing the double power-law fitting functions
of both the unobscured and intrinsic QLFs.
At $z=6-10$, the QLF evolution is produced by the best-fit BH growth model with $\fseed=0.01$.
}
\end{deluxetable*}

%%%%%%%
%    Table. 3
%%%%%%%
\begin{deluxetable*}{lccccccc}%[t!]
\tablecolumns{1}
\renewcommand\thetable{3} %! fix indexing
\tablewidth{0pt} 
\tablecaption{Detection Number of Quasars Estimated for Future Surveys \label{tab:N_detect}} %! reference indexing
\tablehead{
  \colhead{Telescope} & \colhead{ Survey area} & \colhead{Photo. depth} &  \colhead{$N(z\sim 6)$} & \colhead{$N(z\sim 7)$}& \colhead{$N(z\sim 8)$}&  \colhead{$N(z\sim 9)$}&  \colhead{$N(z\sim 10)$}\\
  \colhead{} & \colhead{(\rm{deg}$^2$)} & \colhead{(AB mag)} & & & & & 
}
\startdata
Wide RST    &  2000  & $YJH$  27   & $6759_{-3185}^{+15} $ &  $1514_{-558}^{+169}$ &  $349_{-131}^{53}$ & $85_{-48}^{+23}$ & $25^{+12}_{-15}$  \\
Wide RST    &  2000  & $\Muv=-26$ & $21_{-5}^{+13} $      &  $2_{-7}^{+8}$        &  --  & -- & --  \\
\hline
Wide Euclid & 15000  & $YJH$  24   & $6654^{+95}_{-2282}$  &  $708^{+213}_{-237}$ &   $93^{+66}_{-56}$ & $14^{+32}_{-27}$ & --  \\
Wide Euclid & 15000  & $YJH$  23   & $2480^{+188}_{-614}$  &  $207^{+144}_{-114}$ &   $23^{+27}_{-19}$ & $3^{+12}_{-10}$ & --  \\
Wide Euclid & 15000  & $\Muv=-26$  & $154^{+100}_{-38}$    &  $12^{+59}_{-50}$    &   $1^{+4}_{-3}$    & -- & --  \\
\enddata
\tablecomments{\blue{
Predicted number of quasars by the BH growth model with $\fseed=0.01$ at each redshift in the two surveys, with the assumption of the survey volume with $\Delta z =1$ and 100\% completeness.
The integration of QLF starts from the 5$\sigma$ point source detection limits of the $YJH$ bands in each survey (27 mag for the RST; 24 mag for Euclid), 
and from the bright absolute magnitude with $\Muv<=-26$ mag.
In addition, with more realistic quasar identification capability down to 23 mag in the $YJH$ bands,
\citet{2019Barnett} predicts the yields of quasar numbers as 117 at $7<z<7.5$, 25 at $7.5<z<8.5$, and 2 at $8.5<z<9$.
We set the same detection limit and find our result in good agreement with theirs.}
}
\end{deluxetable*}

@@

In the left panel of Fig.~\ref{fig:BHMF_rhoz}, we show the predicted BHMFs at five different redshifts of $z=6-10$
for $\fseed=0.1$ (solid) and $0.01$ (dashed).
As shown in Fig.~\ref{fig:seedmf}, the mass distribution of seed BHs develops up to $M_\bullet \lesssim 2\times10^5~\Msun$ by $z\gtrsim 17$.
Thus, the high-mass tail of the BHMF is produced owing to subsequent growth of seed BHs (i.e., the fraction $\fseed$ of all the seeds).
In fact, the case with $\fseed=0.1$ yields the number density of those growing seeds ten times higher than that with $\fseed =0.01$,
making the difference in the BH abundance at $M_\bullet \sim 10^{5-6}~\Msun$.
%\footnote{For each case, a fraction $(1-\fseed)$ of BHs are assumed to keep the original mass at birth without subsequent growth.}.
This result suggests that the information on the seeding process still remains in the low mass regime.
Toward lower redshifts, heavier BHs with $\gtrsim 10^7~\Msun$ emerge owing to efficient growth
and thus the number density of such massive BHs in the high-mass tail increases.
Since the BHMF shape at $z=6$ is constrained by \citetalias{2010AJ....140..546W},
% BHMF with $M_\bullet \simeq 10^8-3\times 10^9~\Msun$ at $z=6$,
the two cases reproduce similar shapes of mass distribution at $M_\bullet \simeq 10^8-3\times 10^9~\Msun$ (see Fig.~\ref{fig:fitmf}).
\blue{As a result, the BHMF at $M_\bullet \gtrsim 10^7~\Msun$, which is potentially accessible by quasar observations,
can be characterized with a double power-law function, similar to lower-$z$ quasar populations \citep[e.g.,][]{2013ApJ...764...45K,2015MNRAS.447.2085S}.
}%while the difference in the two BHMF shapes is profound toward the low mass range of $M_\bullet \lesssim 10^7~\Msun$.
%The BH abundance and shape of the mass distribution at $10^5 \lesssim M_\bullet/\Msun \lesssim 10^7$ depend on the seeding fraction,
%while the distributions converge at $M_\bullet \gg 10^7~\Msun$ toward $z= 6$. 
%This result suggests that the information on the seeding process would still remain in the low mass regime of $M_\bullet \lesssim 10^7~\Msun$.
%
%The different seeding fraction varies the characteristic BH mass where the BHMF slope is close to $\alpha_{M_\bullet}\simeq -1$,
%i.e., the typical masses which dominate the cumulative mass density (see Section~\ref{sec:fitting_result}). 
% the difference is also shown by the mass ranges where the slope of BHMF is close to $\alpha_{M_\bullet}\simeq -1$,
%i.e., the typical masses which dominate the cumulative mass density (see Section~\ref{sec:fitting_result}). 
%In the case of $\fseed=0.01$, this typical mass range is higher, despite the integrated mass density is lower than that with $\fseed=0.1$.

>>>>

% \documentclass[linenumbers,preprint2,tighten,trackchanges]{aastex631}
%\documentclass[nolinenumbers,preprint2,tighten]{aastex631}
%\hypersetup{filecolor=cyan,urlcolor=blue} %citecolor=green, linkcolor=red,
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{mathrsfs}

@@

\title{The Assembly of Black Hole Mass ad Luminosity Functions of High-redshift Quasars\\via Multiple Accretion Episodes}

@@

%%%%%%%
%    Fig. 1
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=140mm]{seedBHMF_z.png}
\caption{
Mass distribution of seed BHs formed in quasar host galaxies at different redshifts ($10\leq z \leq 50$).
In each panel, the contribution from newly-born BHs in the redshift interval is highlighted in magenta,
and the cumulative number distribution of BHs formed by prior episodes is shown in green.
The majority of seed BHs form in the epoch of $20\lesssim z \lesssim 40$.
Overall, the distribution is extended to $M_\bullet \gtrsim 10^5~\Msun$, 
imprinted with the halo assembly and environmental effects discussed in Section~\ref{sec:seed}.
}
\label{fig:seedmf}
\vspace{5mm}
\end{figure*}

@@

Fig.~\ref{fig:seedmf} presents how the seed mass function is developed in each redshift interval.
The majority of seed BHs forms in the epoch of $20\lesssim z \lesssim 40$, and the distribution function is 
extended to $M_\bullet \gtrsim 10^5~\Msun$, imprinted with the halo assembly and environmental effects.
Note that we consider massive seed BHs formed from low-metallicity environments,
but neglect a potential contribution from BHs left behind the second-generation star formation
that takes place in metal-enriched environments.
%Finally, we note that in each parent halo, we consider purely the PopIII stellar remnants in the seed BH mass function construction,
%neglecting the BHs formed by the second-generation PopII stars.
%Formed in metal-enriched environments, PopII stellar remnants are more abundant but typically less massive.
The latter ones would dominate in number at the low-mass end of the BHMF at $z\sim 6$,
but have little impacts on the bulk properties of the observed QLF and BHMF \citep[see][]{2022MNRAS.511..616T}.

\vspace{2mm}
\subsection{BH mass growth}
\label{sec:model}
With BH seeds planted, we study the evolution of the BH mass distribution until $z=6$. 
The growth model of each BH is characterized by a minimal number of free parameters, 
giving the accretion rate by
%
\begin{equation}
  \label{eq:mdot}
  \Mdot_\bullet = \lambda f(\Mbh) \Mdot_\mathrm{Edd} ,
\end{equation}
where $\lambda \equiv L/L_\mathrm{Edd}$ is the luminosity-based Eddington ratio,
and $\Mdot_\mathrm{Edd} \equiv L_{\mathrm{Edd}}/\eta_0 c^2$ is the Eddington accretion rate with a radiative efficiency of $\eta_0=0.1$ \citep{1973A&A....24..337S},
which is consistent with the value obtained from the Soltan-Paczy{\'n}ski argument \citep[e.g.,][]{2002MNRAS.335..965Y,2010ApJ...725..388C}.
On the basis of studies on the mass dependence of the radiative efficiency for AGNs at $z\lesssim$ 3 
\citep{2008MNRAS.390..561C,2012ApJ...749..187L,2014ApJ...786..104U}, 
we introduce a similar functional form of
%
\begin{equation}
\label{eq:f_M}
f(\Mbh) = \frac{2}{1+\left(\Mbh /M_{\bullet,c} \right)^\delta}, 
\end{equation}
%
where $M_{\bullet,c}=10^8~\Msun$ is adopted
\footnote[3]{
A series of radiation hydrodynamical simulations for BH accretion
suggest that the gas supplying from galactic scales into the nuclear scale does not sustain 
super-Eddington accretion when the BH mass is higher than the characteristic value \citep{2021ApJ...907...74T}.}.
With a positive value of $\delta$, the BH growth at the high mass end is suppressed,
while the growth speed for less masssive BHs is accelerated.
In the limit of $\delta \ll 1$, where $f(\Mbh) \simeq 1$ is nearly independent of $M_{\bullet,c}$,
the model in Eq.~(\ref{eq:f_M}) reproduces an exponential growth with an $e$-folding timescale of
$t_{\rm S} =  \Mbh/\Mdot_{\mathrm{Edd}} \approx 45$ Myr (the so-called Salpeter timescale; \citealt{1964ApJ...140..796S}).

%%%%%%%
%    Fig. 2
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=170mm]{scheme1.pdf}
\caption{
Schematic illustration of the numerical procedure for calculating the BH mass function
between intervals with a duration of $\tau$.
The time evolution of the distribution is calculated by adding newly-forming seed BHs and 
taking into account growth of existing BHs via mass accretion.
For a given BH population at a checkpoint at $t=T_0$, their growth is calculated with Eqs.~(\ref{eq:dpdm}) and (\ref{eq:mi2m}),
where the ERDF is assumed to follow Eq.~(\ref{eq:Pl}).
For a newly formed seed BH with $M_{\rm k}$ during the interval (i.e., $T_0 \leq t_k < T_0+\tau$), 
we evolve the BH mass in $\Delta t = T_0+\tau -t_k$ and add it to the mass distribution of the existing BH.
}
\label{fig:scheme}
\vspace{8mm}
\end{figure*}

@@

\vspace{2mm}
\subsection{BH mass function}\label{sec:MF}

@@

\vspace{2mm}
\section{Results}\label{sec:fitting_result}

%%%%%%%
%    Fig. 3
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=80mm]{f1_corner.pdf}\hspace{3mm}
\includegraphics[width=80mm]{f2_corner.pdf}
\caption{
Two dimensional posterior distribution of all the model parameters with $\fseed=0.1$ (left) and 0.01 (right), 
along with the marginalized one dimensional projection.
The three vertical dashed lines in the one-dimensional posterior distribution of each parameter correspond to 
16\%, 50\%, and 84\% quantiles in the cumulative distribution, respectively. 
The best-fit values shown with the red lines are listed in Table~\ref{tab:best_fits}.
}
\label{fig:contour}
\vspace{5mm}
\end{figure*}
%

@@

%%%%%%%
%    Table. 1
%%%%%%%
\begin{deluxetable}{cccccccc}%[t!]
\tablecolumns{1}
\renewcommand\thetable{1} %! fix indexing
\tablewidth{0pt}
\tablecaption{Best-fit parameters for BH growth\label{tab:best_fits}} %!!!!
\tablehead{
  \colhead{$\fseed$}  && \colhead{$\tau$ (Myr)} & \colhead{$\delta$} &  \colhead{$\lambda_0$}  & \colhead{$\alpha$}  & \colhead{$\chi^2$}
}
\startdata
1.0    &&  23.13 &    0.001    &   0.96    &   -0.06    &    15.77   \\
0.1    &&  20.07 &    0.001    &   0.89    &    0.12    &    8.27    \\
0.01   &&  18.76 &    0.055    &   0.87    &    0.20    &    6.21    \\
\enddata
\tablecomments{
The best-fit parameters optimized by MCMC sampling for the three different cases of $\fseed$.
The fitting performance is characterized by the relative magnitudes of the $\chi^2$ value.}
\end{deluxetable}

@@

%%%%%%%
%    Fig. 4
%%%%%%%
\begin{figure*}
\centering
%\includegraphics[width=170mm]{fits_MF.png}
\includegraphics[width=85mm]{f1ndraw60MF_spread.pdf}\hspace{3mm}
\includegraphics[width=85mm]{f2ndraw60MF_spread.pdf}
\caption{
The BH mass function at $z=6$ with the best-fit parameters (black curve) and the $1\sigma$ statistical error (grey shaded region) 
for the cases with $\fseed=0.1$ (left) and $0.01$ (right). 
For comparison, the BHMF constructed by \citetalias{2010AJ....140..546W} and their statistical errors (see text) are shown with the cyan curve and shaded region.
}
\label{fig:fitmf}
\vspace{2mm}
\end{figure*}

%%%%%%%
%    Fig. 5
%%%%%%%
\begin{figure*}
\centering
%\includegraphics[width=170mm]{fits_LF.png}
\includegraphics[width=85mm]{f1ndraw60LF_spread.pdf}\hspace{3mm}
\includegraphics[width=85mm]{f2ndraw60LF_spread.pdf}
\caption{
The quasar luminosity function at $z=6$ with the best-fit parameters (black curve) and the $1\sigma$ statistical error (grey shaded region) 
for the cases with $\fseed=0.1$ (left) and $0.01$ (right).
The solid and dashed curves are the unobscured and intrinsic QLF, respectively.
We overlay the observational data for the unobscured QLF taken from \citetalias{2018ApJ...869..150M} in blue and their parametric function with a double power-law function (dotted curve).
Upper bounds of the number density of faint quasars are given by \citet{2022NatAs...6..850J}, based on the Hubble Space Telescope imaging observations (green).
The QLF data based on X-ray selected quasars at $z\sim 5.55$ are overlaid in orange \citep{2019ApJ...884...19G}, for which the normalization is scaled to $z=6$
by a factor of $10^{-0.72\Delta z}$ \citep{2016ApJ...833..222J}, where $\Delta z=0.45$.
}
\label{fig:fitlf}
\vspace{5mm}
\end{figure*}

@@

%%%%%%%
%    Fig. 6
%%%%%%%
\begin{figure*}
\centering
%\includegraphics[width=175mm]{BHMF_rhoz1.png}
\includegraphics[width=85mm]{MF.pdf}\hspace{5mm}
\includegraphics[width=81mm]{rhoM_comb.pdf}
\caption{
{\it Left}: The predicted BH mass functions at $z=6-10$ for the case with $\fseed=0.1$ (solid) and $0.01$ (dashed), including the seed population.
%including a fraction of $\fseed$ seeds evolving by our model assumption and the remaining ($1-\fseed$) fraction with no subsequent growth.
%The solid (dashed) lines denote the cases with $\fseed=0.1$ (0.01).
{\it Right}: the cumulative mass density for BHs in three different mass ranges: $M_\bullet \leq 10^6~\Msun$ (blue), $10^6~\Msun < M_\bullet < 10^8~\Msun$ (orange),
and $M_\bullet \geq 10^8~\Msun$ (green).
The dashed-dotted curve shows the results from the cosmological simulations by \citet{2022MNRAS.513..670N}.
The black arrows present upper bounds of the mass accreted onto BHs obtained from measurements of unresolved cosmic X-ray background radiation \citep{2013ApJ...778..130T}.
}
\label{fig:BHMF_rhoz}
\vspace{5mm}
\end{figure*}

@@

@@

In the left panel of Fig.~\ref{fig:BHMF_rhoz}, we show the predicted BHMFs at five different redshifts of $z=6-10$
for $\fseed=0.1$ (solid) and $0.01$ (dashed).
As shown in Fig.~\ref{fig:seedmf}, the mass distribution of seed BHs develops up to $M_\bullet \lesssim 2\times10^5~\Msun$ by $z\gtrsim 17$.
Thus, the high-mass tail of the BHMF is produced owing to subsequent growth of seed BHs (i.e., the fraction $\fseed$ of all the seeds).
In fact, the case with $\fseed=0.1$ yields the number density of those growing seeds ten times higher than that with $\fseed =0.01$,
making the difference in the BH abundance at $M_\bullet \sim 10^{5-6}~\Msun$.
%\footnote{For each case, a fraction $(1-\fseed)$ of BHs are assumed to keep the original mass at birth without subsequent growth.}.
This result suggests that the information on the seeding process still remains in the low mass regime.
Toward lower redshifts, heavier BHs with $\gtrsim 10^7~\Msun$ emerge owing to efficient growth
and thus the number density of such massive BHs in the high-mass tail increases.
Since the BHMF shape at $z=6$ is constrained by \citetalias{2010AJ....140..546W},
the two cases reproduce similar shapes of mass distribution at $M_\bullet \simeq 10^8-3\times 10^9~\Msun$ (see Fig.~\ref{fig:fitmf}).
As a result, the BHMF at $M_\bullet \gtrsim 10^7~\Msun$, which is potentially accessible by quasar observations,
can be characterized with a double power-law function, 
%
\begin{equation}
\Phi_{M_\bullet}=\frac{\Phi_{M_\bullet}^\ast}{(M_\bullet/M_{\bullet}^\ast)^{-(\hat \alpha+1)} + (M_\bullet/M_{\bullet}^\ast)^{-(\hat \beta+1)}},
\end{equation}
%
similar to lower-$z$ quasar populations \citep[e.g.,][]{2013ApJ...764...45K,2015MNRAS.447.2085S}.
Here, $\Phi_{M_\bullet}^\ast$ (in units of Gpc$^{-3}$ dex$^{-1}$) is the overall normalization, $M_\bullet^\ast$ is the characteristic BH mass,
and $\hat \alpha$ and $\hat \beta$ are the low and high-mass end power-law slopes, respectively.
In Table~\ref{tab:BHMF_fit}, we summarize those parameters of the parametric BHMF at $z=6-10$ for the best-fit models.
%while the difference in the two BHMF shapes is profound toward the low mass range of $M_\bullet \lesssim 10^7~\Msun$.
%The BH abundance and shape of the mass distribution at $10^5 \lesssim M_\bullet/\Msun \lesssim 10^7$ depend on the seeding fraction,
%while the distributions converge at $M_\bullet \gg 10^7~\Msun$ toward $z= 6$. 
%This result suggests that the information on the seeding process would still remain in the low mass regime of $M_\bullet \lesssim 10^7~\Msun$.
%
%The different seeding fraction varies the characteristic BH mass where the BHMF slope is close to $\alpha_{M_\bullet}\simeq -1$,
%i.e., the typical masses which dominate the cumulative mass density (see Section~\ref{sec:fitting_result}). 
% the difference is also shown by the mass ranges where the slope of BHMF is close to $\alpha_{M_\bullet}\simeq -1$,
%i.e., the typical masses which dominate the cumulative mass density (see Section~\ref{sec:fitting_result}). 
%In the case of $\fseed=0.01$, this typical mass range is higher, despite the integrated mass density is lower than that with $\fseed=0.1$.

%%%%%%%
%  Table. 2
%%%%%%%
\begin{deluxetable}{ccccccc}%[t!]
\tablecolumns{1}
\renewcommand\thetable{2} %! fix indexing
\tablewidth{0pt}
\tablecaption{Parametric Black Hole Mass Function \label{tab:BHMF_fit}}
\tablehead{
%  & & \multicolumn{4}{c}{Unobscured QLF} && \multicolumn{4}{c}{Intrinsic QLF}  \\
%  \cline{3-6} \cline{8-11}
  \colhead{Redshift} & \colhead{$\Phi_{M_\bullet}^\ast$} & \colhead{$M_\bullet^\ast$} & \colhead{$\hat \alpha$} & \colhead{$ \hat \beta$}& \\
   & \colhead{(Gpc$^{-3}$ dex$^{-1}$)} & \colhead{($10^7~\Msun$)} & & &
}
\startdata
$z\sim 6$  & $1310$ & $6.13$ & -1.41 & -2.58    & \\
$z\sim 7$  & $166$   & $8.12$ & -1.81 & -2.88    & \\
$z\sim 8$  & $23.2$  & $9.98$ & -2.07 & -3.12    & \\
$z\sim 9$  & $5.61$  & $9.44$ & -2.24 & -3.29    & \\
$z\sim10$  & $2.13$ & $7.68$  & -2.35 & -3.41    & \\
\enddata
\tablecomments{The fitting parameters of the BHMF with 
a double power-law function for the case with $\fseed=0.01$.
The fitted mass range is $10^6~\Msun \leq M_\bullet \leq 10^{10}~\Msun$.
}
\end{deluxetable}
